\chapter{Attachments}

\section{Source Codes}
\label{sec:source-codes}

\xxx{TODO: source codes}

\section{Web Application}
\label{sec:web-application}

The CryptoShow web application is available at \url{https://cryptoshow.cz/}.

\section{API Endpoints}
\label{sec:api-endpoints}

The following list summarizes the API endpoints exposed by the FastAPI server.

\begin{itemize}
    \item \textbf{GET /} - Root endpoint, returns a hello message for debugging.
    \item \textbf{GET /openapi} - Returns the generated OpenAPI schema for the API.
    \item \textbf{GET /gpu-status} - Checks if CUDA is available; returns a task ID for the CUDA Celery test task.
    \item \textbf{GET /health} - Returns the health status of the server (\lstinline|status: healthy|).
    \item \textbf{POST /calculate} - Calculates the prediction for a given PDB/AF ID.
    \item \textbf{POST /calculate-custom} - Calculates the prediction for an uploaded PDB/mmCIF file.
    \item \textbf{GET /task-status/\{task\_id\}} - Checks the status of a Celery task. Returns status and result if available.
    \item \textbf{GET /file/\{task\_hash\}/\{filename\}} - Downloads a file (e.g., results) for a given task.
    \item \textbf{GET /animate/\{task\_hash\}/\{aligned\_structure\_filename\}/\{target\_chains\}} - Creates an animated trajectory file for selected chains and a given structure file.
    \item \textbf{WS /ws/task-status/\{task\_id\}} - WebSocket endpoint for real-time Celery task status updates.
    \item \textbf{POST /proxy/ahoj/job} - Proxies a POST request to \lstinline|apoholo.cz| for job submission.
    \item \textbf{GET /proxy/ahoj/\{task\_hash\}/\{path\}} - Proxies a GET request to \lstinline|apoholo.cz| for file retrieval.
\end{itemize}
